---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.  -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Insert Package Name

<!-- badges: start -->
Profanities in Quentin Tarantino Films
<!-- badges: end -->

The goal of *Profanities in Quentin Tarantino Films* dataset is to provide a viewers guide on the curse words and death in Quentin Tarantino films.

The dataset is the backstage story of the article *A Complete Catalog Of Every Time Someone Cursed Or Bled Out In A Quentin Tarantino Movie*(https://fivethirtyeight.com/features/complete-catalog-curses-deaths-quentin-tarantino-films/)

## Installation

The development version of the dataset is available from [GitHub FiveThirtyEight](https://github.com/fivethirtyeight) with: (https://github.com/fivethirtyeight/data/tree/master/tarantino)

``` r
# install.packages("devtools")
devtools::install_github("Reed-Math241/pkggrpg")
```
## Example


```{r example}
library(tarantino_data)
```




